---
title: "Advanced R visualization"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(funModeling)#plot_num
library(corrplot)
library(dplyr)
library(purrr)
library(ggpubr) #ggarrange
library(lubridate)#MOnth
library(highcharter)
library(ggridges)#geom_density_ridges_gradient
library(viridis)#scale_viridis
library(gridExtra)#grid.arrange
library(forcats)#fct_rev
library(readxl)
library(leaflet)
library(xts)
library(dygraphs)
library(tidyverse)
library(quantmod)
library(RColorBrewer)
library(plotly)
library(clifro)
library(hrbrthemes)
```

```{r}
setwd("C:\\Users\\User\\Google Drive (i.narkevich@student.uw.edu.pl)\\Master degree II year\\Advanced Visualisation in R\\visualizationR")
rain<-read.csv("weatherAUS.csv", sep=",", dec=",", header=TRUE) 
rain <- subset(rain, select = -c(RISK_MM))
```

Basic EDA {data-icon="fa-umbrella"}
=============================

```{r}
#Change the type of variables into numeric
col_num = c(3,4,5,6,7,16,17,20,21)    
rain[,col_num] = apply(rain[,col_num], 2, function(x) as.numeric(as.character(x)))
#Changing format of data 
rain$Date <- as.Date(rain$Date, 
                      format = "%Y-%m-%d")
```

```{r}
rain$Month <- month(rain$Date)
rain$Year <- year(rain$Date)
rain$Month <- as.factor(rain$Month)
rain$Year <- as.factor(rain$Year)
```








Column {data-height=700}
-----------------------------------------------------------------------

### Correlation plot

```{r}
 #define continuous and categorical 
continuous_var <- rain %>% keep(is.numeric)

cor.data <- cor(continuous_var, use="pairwise.complete.obs") 
corrplot.mixed(cor.data, tl.pos = "lt",tl.col = 'black', number.cex=0.55)
```

### Distribution of numeric variables

```{r}
continuous_var <- rain %>% keep(is.numeric)
plot_num(continuous_var)
```



Column {data-height=700}
-----------------------------------------------------------------------

### Relation between categorical variables and probability of raining


```{r}
min_temp<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=MinTemp))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
max_temp<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=MaxTemp))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
rain_fall<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Rainfall))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
evaporation<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Evaporation))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
sunshine<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Sunshine))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
wind_gust_speed<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=WindGustSpeed))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
wind_speed9<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=WindSpeed9am))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
wind_speed3<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=WindSpeed3pm))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
humidity9<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Humidity9am))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
humidity3<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Humidity3pm))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
pressure9<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Pressure9am))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
pressure3<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Pressure3pm))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
cloud9<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Cloud9am))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
cloud3<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Cloud3pm))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
temp9<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Temp9am))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
temp3<-ggplot(data=rain, aes(x=factor(RainTomorrow), y=Temp3pm))+
        geom_boxplot(col='#66B2FF') + labs(x='Rain Tomorrow')
ggarrange(min_temp,max_temp,rain_fall,evaporation,sunshine,wind_gust_speed,wind_speed9,wind_speed3,humidity9,humidity3,pressure9,pressure3,cloud9, cloud3,temp9,temp3)
```

### Relation between categorical variables and probability of raining

```{r}
m_sunshine<-  ggplot(data=rain, aes(Month, Sunshine, fill = Month)) +
  geom_boxplot() +
  theme(legend.position = "none")

m_evaporation<-  ggplot(data=rain,aes(Month, Evaporation, fill = Month)) +
  geom_boxplot() +
  theme(legend.position = "none")

m_windgustspeed<-  ggplot(data=rain,aes(Month, WindGustSpeed, fill = Month)) +
  geom_boxplot() +
  theme(legend.position = "none")

m_windspeed9am<-  ggplot(data=rain,aes(Month, WindSpeed9am, fill = Month)) +
  geom_boxplot() +
  theme(legend.position = "none")

m_humidity9am<-  ggplot(data=rain,aes(Month, Humidity9am, fill = Month)) +
  geom_boxplot() +
  theme(legend.position = "none")

m_pressure9am<-  ggplot(data=rain,aes(Month, Pressure9am, fill = Month)) +
  geom_boxplot() +
  theme(legend.position = "none")

m_cloud9am<-  ggplot(data=rain,aes(Month, Cloud9am, fill = Month)) +
  geom_boxplot() +
  theme(legend.position = "none")

m_temp9am<-  ggplot(data=rain,aes(Month, Temp9am, fill = Month)) +
  geom_boxplot() +
  theme(legend.position = "none")

ggarrange(m_sunshine,m_evaporation,m_windgustspeed,m_windspeed9am,m_humidity9am,m_pressure9am,m_cloud9am,m_temp9am)
```





Temperature {data-icon="fa-thermometer"}
=============================

Column {data-height=100}
-----------------------------------------------------------------------
```{r}
rain_select<-filter(rain, Year != 2007 & Year != 2008 & Year != 2017)

cities <- as.character(sort(unique(rain_select$Location)))
years <- as.character(sort(unique(rain_select$Year)))

selectInput("cities_input", label = "Select City:",
               choices = cities , selected = "Adelaide")

```

```{r}
selectInput("year_input", label = "Select Year:",
               choices = years, selected = "2016")
```

Column {data-height=500}
-----------------------------------------------------------------------

### Temperature during the year

```{r}
renderHighchart({
    rain_f = filter(rain, Location == input$cities_input)#"Adelaide")
  rain_f = filter(rain_f, Year == input$year_input)
  rain_f <- rain_f[c('Date', 'MaxTemp', 'MinTemp')]
  rain_f$MeanTemp <-  (rain_f$MaxTemp+rain_f$MinTemp)/2
  
  x <- c("Min", "Mean", "Max")
  y <- sprintf("{point.%s}", c("MinTemp", "MeanTemp", "MaxTemp"))
  tltip <- tooltip_table(x, y)

  hchart(rain_f, type = "columnrange",
       hcaes(x = Date, low = MinTemp, high = MaxTemp,
             color = MeanTemp)) %>%
  hc_chart(polar = TRUE) %>%
  hc_yAxis( max = 40, min = 0, labels = list(format = "{value} C"),
            showFirstLabel = FALSE) %>%
  hc_xAxis(
    title = list(text = ""), gridLineWidth = 0.5,
    labels = list(format = "{value: %b}")) %>%
  hc_tooltip(useHTML = TRUE, pointFormat = tltip,
             headerFormat = as.character(tags$small("{point.x:%d %B, %Y}")))

})

```

### The distribution max and min temperature by months

```{r}
p1 <- rain %>%
  ggplot(aes(x = MaxTemp, y = fct_rev(Month), fill = ..x..)) +
  geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01, gradient_lwd = 1., bandwidth = 1.4) +
  #scale_fill_viridis(name = "T_max [?C]", option = "C") +
  scale_fill_continuous(low = "#EAF353", high = "#F6AA68") +
  ggtitle("Max temperature by months") +
  labs(x = "Maximum temperature", y = "") +
  theme_ridges(font_size = 13, grid = TRUE) +
  theme(legend.position = "none") +
  theme(axis.title.y = element_blank())

p2 <- rain %>%
 ggplot(aes(x = MinTemp, y =fct_rev(Month), fill = ..x..)) +
 geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01, gradient_lwd = 1., bandwidth = 4) +
 scale_fill_continuous(low = "#8370EE", high = "#4E6587") +
 ggtitle("Min temperature by months") +
labs(x = "Minimum temperature", y = "", fill = "Humidity") +
 theme_ridges(font_size = 13, grid = TRUE) +
 theme(legend.position = "none") +
 theme(axis.title.y = element_blank())

grid.arrange(p1,p2, ncol = 2, nrow = 1)

```




Column {}
-----------------------------------------------------------------------
### Temperature at 9am and 3pm

```{r}
renderDygraph({
  #rain_f = filter(rain, Location == input$cities_input)
  rain1 = filter(rain, Location == input$cities_input)
  temp <- cbind(rain1$Temp9am, rain1$Temp3pm)
  colnames(temp) <- c("9am", "3pm")
  m.xts <- xts(temp, order.by=rain1$Date)

  dygraph(m.xts, main = "Temperature") %>%
  dyOptions(colors = c("#3399FF", "#00008b"))%>%
  dySeries("3pm", axis = "y2") %>%
  dyAxis(name = "y",
         label = "Temperature at 9am",
         axisLabelFontSize = 10) %>%
  dyAxis(name = "y2",
         label = "Temperature at 3pm",
         axisLabelFontSize = 10) %>%
  dyRangeSelector(dateWindow = c("2008-02-17", "2017-06-15"),
                   fillColor = "#3399FF")}) 
```





Sunshine {data-icon="fa-sun"}
=============================

Row
-----------------------------------------------------------------------

### The average number of hours of bright sunshine in the day.

```{r}
articles <- round(mean(rain$Sunshine, na.rm = TRUE),1)
valueBox(articles, icon = "fa-calendar", color = "#99CCFF")
```

### The sunniest city.

```{r}
rain_sun<-rain %>%
  group_by(Location) %>%
  summarise(mean=mean(Sunshine, na.rm = T)) %>% as.data.frame()

sunniest_city<-rain_sun[which.max(rain_sun$mean),]$Location

valueBox(sunniest_city, icon = "fa-sun", color = "#66B2FF")
```

### The least sunny city.

```{r}
darkest_city<-rain_sun[which.min(rain_sun$mean),]$Location
valueBox(darkest_city, 
         icon = "fa-cloud",
         color = "#3399ff")
```


Row {}
-----------------------------------------------------------------------

### Sunshine across cities 
```{r}
city<-read_xlsx("cities.xlsx")


mean_sunshine<-rain %>%

  group_by(Location) %>%
  summarise(mean=mean(Sunshine, na.rm = T)) %>% as.data.frame()

total_list <- merge(mean_sunshine, city, by="Location")
```

```{r}
pal <- colorNumeric(
  palette = "YlGnBu",
  domain = total_list$mean
)


qpal <- colorQuantile("YlOrRd", total_list$mean, n = 7)

leaflet(total_list) %>%
 addTiles() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addScaleBar() %>%
  addCircleMarkers(~Longitude, ~Latitude, group = "Location",
                   color=~pal(mean), fillOpacity = 0.8, popup = ~as.character(Location), label = ~as.character(Location))%>%
  leaflet::addLegend("bottomright", pal = pal, values = ~mean,title = "Sunshine",opacity = 0.9, labFormat = labelFormat())
```






Rain {data-icon="fa-tint"}
=============================

Column {data-height=100}
-----------------------------------------------------------------------

```{r}
#Data preparation
rain<-as.data.frame(rain)
count_sunshine<-rain %>%
  group_by(Month, Location, RainToday, Year) %>% 
  count(Rainy_days_per_month =n(), na.rm = T) %>% filter(RainToday =="Yes") %>% as.data.frame()

mean_sunshine<-rain %>%
  group_by(Location,Month) %>%
  summarise(mean_sun=mean(Sunshine, na.rm = T)) %>% as.data.frame()

```

```{r}
cities2 <- as.character(sort(unique(na.omit(mean_sunshine)$Location)))
selectInput("cities_input2", label = "Select City:",
               choices = cities2, selected = "Adelaide")

```

```{r}
selectInput("year_input2", label = "Select Year:",
               choices = years, selected = "2008")
```

Column {}
-----------------------------------------------------------------------

### Bubble plot
```{r}
renderPlotly({
  
  total<-merge(mean_sunshine,count_sunshine,by=c("Location", "Month")) %>% na.omit() %>%
  filter(Location ==input$cities_input2 & Year == input$year_input2)%>%
  mutate(Rainy_days_per_month=round(Rainy_days_per_month,1)) %>%
  mutate(mean_sun=round(mean_sun,1)) %>%
  # prepare text for tooltip
  mutate(text = paste("City: ", Location, "\nSunshine: ", mean_sun, "\nRainy days: ", Rainy_days_per_month))
  
  plot <-
  #make a plot
  ggplot(total, aes(x=Month, y=Rainy_days_per_month, size = mean_sun,text=text)) +
  geom_point(alpha=0.5, color="#335DFF" ) +
  scale_size(range = c(3, 8), name="Average amount of\nsunshine per day") +
  ggtitle("The amount of rainy days and sunshine by city and year")+
  #scale_color_viridis(discrete=TRUE, guide=FALSE) +
 # theme_ipsum() +
  theme(legend.position = 'bottom')+
  guides(shape = guide_legend(override.aes = list(size = 10)))


# turn ggplot interactive with plotly
pp <- ggplotly(plot, tooltip="text")%>%
layout(legend = list(orientation = "h", x = -0.5, y =-1))
pp
})

```




Pressure {data-icon="fa-tachometer-alt"}
=============================



```{r}
### Creating seasons
rain5<-rain
rain5$Season <- NA
rain5$Season[rain5$Month == 9 | rain5$Month == 10 | rain5$Month == 11 ] <- 'Spring'
rain5$Season[rain5$Month == 12 | rain5$Month == 1 | rain5$Month == 2 ] <- 'Summer'
rain5$Season[rain5$Month == 3 | rain5$Month == 4 | rain5$Month == 5 ] <- 'Autumn'
rain5$Season[rain5$Month == 6 | rain5$Month == 7 | rain5$Month == 8 ] <- 'Winter'
rain5$Season <- as.factor(rain5$Season)

#Count mean of pressure by seasons
mean_preassure <- aggregate(rain5$Pressure9am, by=list(Season=rain5$Season), FUN=mean, na.rm = T)
```

Column {data-height=350}
-----------------------------------------------------------------------
### Pressure(hpa) in autumn (9am)

```{r}
#1st plot autumn
plot_ly(
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = mean_preassure[1,2],
  title = list(text = mean_preassure[1,1]),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis = list(range = list(800, 1200), tickwidth = 1, tickcolor = "darkblue"),
    bar = list(color = "darkblue"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray",
    steps = list(
      list(range = c(800, 900), color = "99CCFF"),
      list(range = c(900, 1000), color = "66B2FF"),
      list(range = c(1000,1100), color = "3399FF"),
      list(range = c(1100,1200), color = "0080FF")))) %>%
  layout(
    margin = list(l=20,r=30),
    font = list(color = "darkblue", family = "Arial"))

```

### Pressure(hpa) in spring (9am)

```{r}

#2st plot spring
plot_ly(
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = mean_preassure[2,2],
  title = list(text = mean_preassure[2,1]),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis = list(range = list(800, 1200), tickwidth = 1, tickcolor = "darkblue"),
    bar = list(color = "darkblue"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray",
    steps = list(
      list(range = c(800, 900), color = "99CCFF"),
      list(range = c(900, 1000), color = "66B2FF"),
      list(range = c(1000,1100), color = "3399FF"),
      list(range = c(1100,1200), color = "0080FF")))) %>%
  layout(
    margin = list(l=20,r=30),
    font = list(color = "darkblue", family = "Arial"))


```

### Pressure(hpa) in summer (9am)

```{r}

#3st plot summer
plot_ly(
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = mean_preassure[3,2],
  title = list(text = mean_preassure[3,1]),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis = list(range = list(800, 1200), tickwidth = 1, tickcolor = "darkblue"),
    bar = list(color = "darkblue"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray",
    steps = list(
      list(range = c(800, 900), color = "99CCFF"),
      list(range = c(900, 1000), color = "66B2FF"),
      list(range = c(1000,1100), color = "3399FF"),
      list(range = c(1100,1200), color = "0080FF")))) %>%
  layout(
    margin = list(l=20,r=30),
    font = list(color = "darkblue", family = "Arial"))

```

### Pressure(hpa) in winter (9am)

```{r}

#4st plot winter 
plot_ly(
  
  domain = list(x = c(0, 1), y = c(0, 1)),
  value = mean_preassure[4,2],
  title = list(text = mean_preassure[4,1]),
  type = "indicator",
  mode = "gauge+number",
  gauge = list(
    axis = list(range = list(800, 1200), tickwidth = 1, tickcolor = "darkblue"),
    bar = list(color = "darkblue"),
    bgcolor = "white",
    borderwidth = 2,
    bordercolor = "gray",
    steps = list(
      list(range = c(800, 900), color = "99CCFF"),
      list(range = c(900, 1000), color = "66B2FF"),
      list(range = c(1000,1100), color = "3399FF"),
      list(range = c(1100,1200), color = "0080FF")))) %>%
  layout(
    margin = list(l=20,r=30),
    font = list(color = "darkblue", family = "Arial"))


```




Column {data-height=100}
-----------------------------------------------------------------------
```{r}
selectInput("cities_input1", label = "Select City:",
               choices = cities , selected = "Adelaide")
```


Column {}
-----------------------------------------------------------------------

### Pressure 

```{r}

renderDygraph({
  rain1 = filter(rain, Location == input$cities_input1)
  pressure <- cbind(rain1$Pressure9am, rain1$Pressure3pm)
  colnames(pressure) <- c("9am", "3pm")
  m.xts <- xts(pressure, order.by=rain1$Date)

  dygraph(m.xts, main = "Pressure") %>%
  dyOptions(colors = c("#3399FF", "#00008b"))%>%
  dySeries("3pm", axis = "y2") %>%
  dyAxis(name = "y",
         label = "Pressure at 9am",
         axisLabelFontSize = 10) %>%
  dyAxis(name = "y2",
         label = "Pressure at 3pm",
         axisLabelFontSize = 10) %>%
  dyRangeSelector(dateWindow = c("2008-02-17", "2017-06-15"),
                   fillColor = "#3399FF")
  }) 
```




Wind {data-icon="fa-compass"}
=============================

Column {data-height=100}
-----------------------------------------------------------------------
```{r}
selectInput("cities_input3", label = "Select City:",
               choices = cities , selected = "Adelaide")
```


Column {}
-----------------------------------------------------------------------

### Wind at 9am

```{r Wind Rose}

renderPlot({
  
  rain3 = filter(rain, Location == input$cities_input3)
  
  rain3$newWind = rain3$WindDir9am
  
  rain3$newWind<-as.numeric(rain3$newWind)
  
  rain3$newWind[rain3$newWind == 1 ] <- 90 
  rain3$newWind[rain3$newWind == 4] <- 0
  rain3$newWind[rain3$newWind == 2] <- 67.5
  rain3$newWind[rain3$newWind == 3] <- 112.5
  rain3$newWind[rain3$newWind == 5] <- 45
  rain3$newWind[rain3$newWind == 6] <- 22.5
  rain3$newWind[rain3$newWind == 7] <- 337.5
  rain3$newWind[rain3$newWind == 8] <- 315
  rain3$newWind[rain3$newWind == 9] <- 180
  rain3$newWind[rain3$newWind == 10] <- 135
  rain3$newWind[rain3$newWind == 11] <- 157.5
  rain3$newWind[rain3$newWind == 12] <- 202.5
  rain3$newWind[rain3$newWind == 13] <- 225
  rain3$newWind[rain3$newWind == 14] <- 270
  rain3$newWind[rain3$newWind == 15] <- 292.5
  rain3$newWind[rain3$newWind == 16] <- 247.5
  

  Wind_at9am<- windrose(speed = rain3$WindSpeed9am,
         direction =rain3$newWind,
         speed_cuts = seq(0,25,5),
         ggtheme='grey',
         calm_wind = 0, 
         variable_wind = 990,
         legend_title = "Wind Speed\n(km/hr)",
         col_pal = "YlOrBr")

  Wind_at9am
})

```

### Wind at 3pm
```{r}

renderPlot({
  
rain3 = filter(rain, Location == input$cities_input3)
rain3$newWind2 = rain3$WindDir3pm
rain3$newWind2<-as.numeric(rain3$newWind2)

rain3$newWind2[rain3$newWind2 == 1 ] <- 90 
rain3$newWind2[rain3$newWind2 == 4] <- 0
rain3$newWind2[rain3$newWind2 == 2] <- 67.5
rain3$newWind2[rain3$newWind2 == 3] <- 112.5
rain3$newWind2[rain3$newWind2 == 5] <- 45
rain3$newWind2[rain3$newWind2 == 6] <- 22.5
rain3$newWind2[rain3$newWind2 == 7] <- 337.5
rain3$newWind2[rain3$newWind2 == 8] <- 315
rain3$newWind2[rain3$newWind2 == 9] <- 180
rain3$newWind2[rain3$newWind2 == 10] <- 135
rain3$newWind2[rain3$newWind2 == 11] <- 157.5
rain3$newWind2[rain3$newWind2 == 12] <- 202.5
rain3$newWind2[rain3$newWind2 == 13] <- 225
rain3$newWind2[rain3$newWind2 == 14] <- 270
rain3$newWind2[rain3$newWind2 == 15] <- 292.5
rain3$newWind2[rain3$newWind2 == 16] <- 247.5

Wind_at3pm<- windrose(speed = rain3$WindSpeed3pm,
         direction =rain3$newWind2,
         speed_cuts = seq(0,25,5),
         ggtheme='grey',
         calm_wind = 0, 
         variable_wind = 990,
         legend_title = "Wind Speed\n(km/hr)",
         col_pal = "YlOrBr") 

Wind_at3pm
})
```



Humidity {data-icon="fa-cloud"}
=============================


Column {data-height=100}
-----------------------------------------------------------------------
```{r}
selectInput("cities_input4", label = "Select City:",
               choices = cities , selected = "Adelaide")
```

Column {data-height=500}
-----------------------------------------------------------------------

### Humidity

```{r}
#barplot(1:10, col = wes_palette("Zissou1", 10, type = "continuous"))

rain6 <- rain
library(ggpubr)
renderPlot({
  rain6 = filter(rain, Location == input$cities_input4)
  ggscatterhist(
  rain6, x = "Humidity3pm", y = "Temp3pm",
  color = "RainTomorrow", size = 3, alpha = 1,
  palette = c("darkblue", "#3399FF"),
  margin.params = list(fill = "RainTomorrow", color = "black", size = 0.2)
  )
})

```



Column {data-height=500}
-----------------------------------------------------------------------

### Humidity

```{r}
renderDygraph({
  rain1 = filter(rain, Location == "Sydney")
  rain5 = filter(rain, Location == input$cities_input4)
  pressure <- cbind(rain5$Humidity9am, rain5$Humidity3pm)
  colnames(pressure) <- c("9am", "3pm")
  
  m.xts <- xts(pressure, order.by=rain5$Date)
  index(m.xts)
  
  dygraph(m.xts, main = "Humidity") %>%
  dyOptions(colors = c("#3399FF", "#00008b"))%>%
  dySeries("3pm", axis = "y2") %>%
  dyAxis(name = "y",
         label = "Humidity",
         axisLabelFontSize = 10) %>%
  dyRangeSelector(dateWindow = c("2008-02-17", "2017-06-15"),
                   fillColor = "#3399FF")
  }) 
```

